Metadata control document

### 2023-05-04 metadata/metadata_control.Rmd
Cleaning up metadata pre-rerun

---
title: "Metadata control"
author: "William Kumler"
date: "5/5/2022"
output: html_document
---

@@

options(pillar.sigfig = 7)
```

```{r functions}
toDecDeg <- function(deg, min, dir){
  num <- deg+min/60
  if(dir%in%c("S", "W")){
    num*-1
  } else {
    num
  }
}
```

@@

```{r station_metadata}
# DCMs are entered manually ----
if(!file.exists("raw_data/all_DCMs.csv")){
  falkor_DCMs <- data.frame(
    station=c(62, 64, 77, 80),
    cast=1,
    DCM_depth=c(98, 115, 125, 120)
  )
  transect_DCMs <- data.frame(
    station = c(4:13, 13, 14),
    cast=c(1,1,3,1,1,2,2,2,1,2,3,2),
    DCM_depth=c(100, 122, 119, 133, 122, 110, 110, 110, 103, 112, 112, 105)
  )
  center_DCMs <- data.frame(
    station = paste0("L", c(1,1,2,2)),
    cast=c(32, 33, 1, 2),
    DCM_depth=c(108, 104, 123, 123)
  )
  all_DCMs <- rbind(falkor_DCMs, transect_DCMs, center_DCMs)

@@

```{r}
clean_stans <- read.csv(file = "made_data/clean_stans.csv")

culture_desc <- readxl::read_xlsx("raw_data/Heal_mSystems uncorrected Metabs_SuppTabs_20210223.xlsx",
                  sheet = "S7_Culturedescriptions_full")
culture_data <- readxl::read_xlsx("raw_data/Heal_mSystems uncorrected Metabs_SuppTabs_20210223.xlsx",
                                  sheet = "S5_FullEnviroCulture_PeakAreas")
taxa_metabs <- culture_data %>%
  filter(!str_detect(MassFeature_Column, "RP$")) %>%
  mutate(polarity=tolower(str_extract(MassFeature_Column, "Neg$|Pos$"))) %>%
  select(Identification, polarity, `7803_B`:Nmar_3) %>%
  pivot_longer(cols = `7803_B`:Nmar_3) %>%
  left_join(clean_stans %>% select(compound_name, compound_name_old, polarity), 
            by=c(Identification="compound_name_old", "polarity")) %>%
  filter(!is.na(compound_name)) %>%
  left_join(culture_desc %>% select(name=`Sample ID`, taxa=`Broad taxon`, species=Species),
            by="name") %>%
  filter(!is.na(value)) %>%
  select(compound_name, polarity, broad_taxa=taxa, species, id=name, value)

>>>>

---
title: "Metadata control document"
author: "William Kumler"
date: "5/5/2023"
output: html_document
---

@@

options(pillar.sigfig = 7)

toDecDeg <- function(deg, min, dir){
  num <- deg+min/60
  if(dir%in%c("S", "W")){
    num*-1
  } else {
    num
  }
}
```

@@

```{r station_metadata}
# DCM depths are entered manually ----
if(!file.exists("raw_data/all_DCMs.csv")){
  falkor_DCMs <- data.frame(
    station=c(62, 64, 77, 80),
    cast=1,
    DCM_depth=c(98, 115, 125, 120)
  )
  transect_DCMs <- data.frame(
    station = c(4:13, 13, 14),
    cast=c(1,1,3,1,1,2,2,2,1,2,3,2),
    DCM_depth=c(100, 122, 119, 133, 122, 110, 110, 110, 103, 112, 112, 105)
  )
  center_DCMs <- data.frame(
    station = paste0("L", c(1,1,2,2)),
    cast=c(32, 33, 1, 2),
    DCM_depth=c(108, 104, 123, 123)
  )
  all_DCMs <- rbind(falkor_DCMs, transect_DCMs, center_DCMs)

@@

```{r}
download.file("https://datadryad.org/stash/downloads/file_stream/2192675", 
              destfile = "raw_data/Heal_mSystems_Supplement.xlsx", 
              mode = "wb")
clean_stans <- read.csv(file = "made_data/clean_stans.csv")

culture_desc <- readxl::read_xlsx("raw_data/Heal_mSystems_Supplement.xlsx",
                  sheet = "S7_Culturedescriptions_full")
culture_data <- readxl::read_xlsx("raw_data/Heal_mSystems_Supplement.xlsx",
                                  sheet = "S5_FullEnviroCulture_PeakAreas")
taxa_metabs <- culture_data %>%
  filter(!str_detect(MassFeature_Column, "RP$")) %>%
  mutate(polarity=tolower(str_extract(MassFeature_Column, "Neg$|Pos$"))) %>%
  select(Identification, polarity, `7803_B`:Nmar_3) %>%
  pivot_longer(cols = `7803_B`:Nmar_3) %>%
  left_join(clean_stans %>% select(compound_name, compound_name_old, polarity), 
            by=c(Identification="compound_name_old", "polarity")) %>%
  filter(!is.na(compound_name)) %>%
  left_join(culture_desc %>% select(name=`Sample ID`, taxa=`Broad taxon`, species=Species),
            by="name") %>%
  filter(!is.na(value)) %>%
  select(compound_name, polarity, broad_taxa=taxa, species, id=name, value)
